---
title: "hw6"
author: "Bijon Setyawan Raya"
date: "4/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
```

# Data Preparation

```{r}
m1 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media1.csv")
m2 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media2.csv")
m3 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media3.csv")
m4 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media4.csv")
media <- rbind(m1,m2,m3,m4)
```

# Question 1) Let’s describe and visualize the data:

## a. What are the means of viewers intentions to share (INTEND.0) for each media type? (report four means)

Here is the mean of `INTEND.0` in each data set: (starting from media1 all the way to media4)

1. `media1$INTEND.0` mean: `r mean(m1$INTEND.0)`
2. `media2$INTEND.0` mean: `r mean(m2$INTEND.0)`
3. `media3$INTEND.0` mean: `r mean(m3$INTEND.0)`
4. `media4$INTEND.0` mean: `r mean(m4$INTEND.0)`

## b. Visualize the distribution and mean of intention to share, across all four media.

```{r cars}
test <- 
  c("animation + audio", "pictures + audio", "pictures + text", "text only")

boxplot(
  INTEND.0 ~ media, 
  data=media, 
  main="Distribution by Media", 
  xlab="Intention", 
  ylab="Media", 
  col="steelblue", 
  border="black", 
  horizontal = TRUE
)
```

## c. From the visualization alone, do you feel that media type makes a difference on intention to share?

# Question 2) Let’s try traditional one-way ANOVA:

## a. State the null and alternative hypotheses when comparing INTEND.0 across four groups in ANOVA

## b. Produce the traditional F-statistic for our test

## c. What are the cut-off values of F for 95% and 99% confidence according the the null distribution of F?

## d. According to the traditional ANOVA, do the four types of media produce the same mean intention to share, at 95% confidence? How about at 99% confidence?

## e. Do you feel the classic requirements of one-way ANOVA are met?