---
title: "hw6"
author: "Bijon Setyawan Raya"
date: "4/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
```

# Data Preparation

```{r}
# Import data sets in Linux
# m1 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media1.csv")
# m2 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media2.csv")
# m3 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media3.csv")
# m4 <- read.csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw6/pls-media4.csv")

m1 <- read.csv("/Users/bijonsetyawan/Documents/Git/bacs-hw/hw6/pls-media1.csv")
m2 <- read.csv("/Users/bijonsetyawan/Documents/Git/bacs-hw/hw6/pls-media2.csv")
m3 <- read.csv("/Users/bijonsetyawan/Documents/Git/bacs-hw/hw6/pls-media3.csv")
m4 <- read.csv("/Users/bijonsetyawan/Documents/Git/bacs-hw/hw6/pls-media4.csv")

media <- rbind(m1,m2,m3,m4)
```

# 1. Let’s describe and visualize the data:

## a. What are the means of viewers intentions to share (INTEND.0) for each media type? (report four means)

\textcolor{red} {Here is the mean of} `INTEND.0` \textcolor{red} {in each data set: (starting from media1 all the way to media4)}

1. `media1$INTEND.0` \textcolor{red} {mean:} `r mean(m1$INTEND.0)`
2. `media2$INTEND.0` \textcolor{red} {mean:} `r mean(m2$INTEND.0)`
3. `media3$INTEND.0` \textcolor{red} {mean:} `r mean(m3$INTEND.0)`
4. `media4$INTEND.0` \textcolor{red} {mean:} `r mean(m4$INTEND.0)`

## b. Visualize the distribution and mean of intention to share, across all four media.

```{r}
boxplot(
  INTEND.0 ~ media, 
  data=media, 
  main="Distribution by Media", 
  xlab="Intention", 
  ylab="Media", 
  col="steelblue",  
  border="black", 
  horizontal = TRUE
)

x0s <- 1:4 - 0.4
x1s <- 1:4 + 0.4
y0s <- c(mean(m1$INTEND.0), mean(m2$INTEND.0), mean(m3$INTEND.0), mean(m4$INTEND.0))
segments(x0=y0s, y0=x0s, y1=x1s, col = "red")
```

## c. From the visualization alone, do you feel that media type makes a difference on intention to share?

\textcolor{red} {In my opinion, the media won't affect the difference on intention to share since the} `grand_mean` \textcolor{red} {value is} `r mean(media$INTEND.0)`.

# 2. Let’s try traditional one-way ANOVA:

## a. State the null and alternative hypotheses when comparing INTEND.0 across four groups in ANOVA

**Null hypothesis** \textcolor{red} {is the means of INTEND.0 in the four data sets are similar to each other. While the} **Alternative hypothesis** \textcolor{red} {is the means of INTEND.0 in the four data sets are not similar to each other.}

## b. Produce the traditional F-statistic for our test

```{r}
grand_mean <- mean(media$INTEND.0)

intend0 <- tibble(
  media = c(1,2,3,4),
  instances = c(
    nrow(m1), 
    nrow(m2), 
    nrow(m3), 
    nrow(m4)
  ),
  group_mean = c(
    mean(m1$INTEND.0),
    mean(m2$INTEND.0), 
    mean(m3$INTEND.0), 
    mean(m4$INTEND.0)
  ),
  var = c(
    var(m1$INTEND.0),
    var(m2$INTEND.0),
    var(m3$INTEND.0),
    var(m4$INTEND.0)
  ),
  sstr = c(
    nrow(m1) * (mean(m1$INTEND.0) - grand_mean)^2,
    nrow(m2) * (mean(m2$INTEND.0) - grand_mean)^2,
    nrow(m3) * (mean(m3$INTEND.0) - grand_mean)^2,
    nrow(m4) * (mean(m4$INTEND.0) - grand_mean)^2
  ),
  sse = c(
    (nrow(m1) - 1) * sd(m1$INTEND.0)^2,
    (nrow(m2) - 1) * sd(m2$INTEND.0)^2,
    (nrow(m3) - 1) * sd(m3$INTEND.0)^2,
    (nrow(m4) - 1) * sd(m4$INTEND.0)^2
  ),
)

intend0
```

```{r}
n <- 4
sstr <- sum(intend0$sstr)
mstr <- sstr/(n-1)
sse <- sum(intend0$sse)
mse <- sse/(nrow(media) - n)
f <- mstr / mse
```

\textcolor{red} {The F-statistics value is} `r f`.

## c. What are the cut-off values of F for 95% and 99% confidence according the the null distribution of F?

\textcolor{red} {The cut-off value of F for 95\% is} `r qf(0.95, df1 = n - 1, df2 = nrow(media) - 1)`\textcolor{red} {, and the cut-off value of F for 99\% is} `r qf(0.99, df1 = n - 1, df2 = nrow(media) - 1)`.

## d. According to the traditional ANOVA, do the four types of media produce the same mean intention to share, at 95% confidence? How about at 99% confidence?

\textcolor{red} {From the (b) and (c), we can see that the f-value doesn't go across 95\% and 99\% cutoff values, we shouldn't reject the null hypothesis. In the other words, we can say that each media has the same mean value.}

## e. Do you feel the classic requirements of one-way ANOVA are met?

Here are the requirements of one-way ANOVA:

1. Variance Equality – That the variance of data in the different groups should be the same.
2. Normality – That each sample is taken from a normally distributed population.

```{r}
intend0$var
```

\textcolor{red} {First, we can see above that, the variance from each data set quite differs from each other.}

```{r}
plot(
  density(m1$INTEND.0), 
  lwd = 2, 
  col = "black", 
  ylim = c(0, 0.30), 
  main = "Distribution of INTEND.0 from 4 Datasets"
)
lines(density(m2$INTEND.0), lwd = 2, col = "coral3")
lines(density(m3$INTEND.0), lwd = 2, col = "blue")
lines(density(m4$INTEND.0), lwd = 2, col = "red")
legend(
  -0.5,
  0.30,
  c("Media 1", "Media 2", "Media 3", "Media 4"),
  lwd = c(2,2,2,2),
  lty = c("solid", "solid", "solid", "solid"),
  col = c("black", "coral3", "blue", "red")
)
```

\textcolor{red} {Second, from the graphs above, clearly the data sets are normally distributed. Thus, the classic requirements of one-way ANOVA are not met.}

# 3. Let's try bootstrapping ANOVA

## a. Bootstrap the null values of F and also the alternative values of the F-statistic.

```{r}
boot_anova <- function(t1, t2, t3, t4, treat_nums) {
  null_sample <- c(
    sample(t1 - mean(t1), length(t1), replace = TRUE),
    sample(t2 - mean(t2), length(t2), replace = TRUE),
    sample(t3 - mean(t3), length(t3), replace = TRUE),
    sample(t4 - mean(t4), length(t4), replace = TRUE)
  )
  
  alt_sample <- c(
    sample(t1, length(t1), replace = TRUE),
    sample(t2, length(t2), replace = TRUE),
    sample(t3, length(t3), replace = TRUE),
    sample(t4, length(t4), replace = TRUE)
  )
  
  c(
    oneway.test(null_sample ~ treat_nums, var.equal = TRUE)$statistic,
    oneway.test(alt_sample ~ treat_nums, var.equal = TRUE)$statistic
  )
}

f_values <- replicate(5000, boot_anova(m1$INTEND.0, m2$INTEND.0, m3$INTEND.0, m4$INTEND.0, media$media))

f_nulls <- f_values[1,]
f_alts <- f_values[2,]
```

## b. From the bootstrapped null values of F, What are the cutoff values for 95% and 99% confidence?

```{r}
quantile(f_nulls, 0.95)
quantile(f_nulls, 0.99)
```

## c. Visualize the distribution of bootstrapped null values of F, the 95% and 99% cutoff values of F, and also the original F-value from bootstrapped alternative values.

```{r}
plot(
  density(f_nulls), 
  col = "black", 
  lwd = 2, 
  main = "Null Values Distribution"
)
abline(v = quantile(f_nulls, 0.95), col="blue", lty = "dashed")
abline(v = quantile(f_nulls, 0.99), col="red",lty = "dashed")
abline(v = mean(f_nulls), col = "green", lty = "dashed")
legend(
  5,
  0.68,
  c("Null Value ", "Mean Value", "95% Cutoff", "99% Cutoff"),
  lwd = c(2,1,1,1),
  lty = c("solid", "dashed", "dashed", "dashed"),
  col = c("black", "green", "blue", "red")
)
```

```{r}
plot(
  density(f_alts), 
  col = "black", 
  lwd = 2, 
  main = "Alternative Values Distribution"
)
abline(v = mean(f_alts), col="red", lty = "dashed")
legend(
  11,
  0.20,
  c("Alternative Value", "Mean"),
  lwd = c(2,1),
  lty = c("solid", "dashed"),
  col = c("black", "red")
)
```

## d. According to the bootstrap, do the four types of media produce the same mean intention to share. at 95% confidence and at 99% confidence?

```{r, echo=FALSE}
plot(
  density(f_nulls), 
  col = "black", 
  lwd = 2, 
  main = "Null Values Distribution"
)
abline(v = quantile(f_nulls, 0.95), col="blue", lty = "dashed")
abline(v = quantile(f_nulls, 0.99), col="red",lty = "dashed")
abline(v = mean(f_nulls), col = "green", lty = "dashed")
legend(
  5,
  0.68,
  c("Null Value ", "Mean Value", "95% Cutoff", "99% Cutoff"),
  lwd = c(2,1,1,1),
  lty = c("solid", "dashed", "dashed", "dashed"),
  col = c("black", "green", "blue", "red")
)
```

Since the graph above shows that the mean of null distribution is way behind the 95% cutoff value, let alone 99%. Thus we can say that these 4 medias produce the same mean intention to share.