---
title: "BACS HW16"
author: '109062710'
date: "6/8/2021"
output: html_document
---

```{r, include = FALSE}
library(seminr)
```

prepare data set

```{r}
sec = read.csv("/home/johnbjohn/Documents/git-repos/bacs-hw/hw16/security_data_sem.csv")
```

# Question 1

## a. Create a PLS path model using SEMinR

### i. Create a measurement model

```{r}
sec_mm <- constructs(
  composite('TRUST', multi_items('TRST', 1:4)),
  composite('SEC', multi_items('PSEC', 1:4)),
  composite('REP', multi_items('PREP', 1:4)),
  composite('INV', multi_items('PINV', 1:3)),
  composite('POL', multi_items('PPSS', 1:3)),
  composite('FAML', single_item('FAML1')),
  interaction_term(iv='REP', moderator='POL', method=orthogonal)
)
```

### ii. Create a structural model

```{r}
sec_sm <- relationships(
  paths(from = c("REP","INV","POL","FAML","REP*POL"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
)
```

```{r}
pls <- estimate_pls(
  data = sec,
  measurement_model = sec_mm,
  structural_model = sec_sm
)

pls_report <- summary(pls)

pls_report
```

## b. Show the results in table format

### i. plot a figure of the estimated model

```{r}
plot(pls, title="PLS plot")
```

### ii. Weights and loadings of composites

Weight of composites

```{r}
pls_report$weights
```

Loading of composites

```{r}
pls_report$loadings
```

### iii. Regression coefficients of paths between factors

```{r}
pls_report$paths
```

### iv. Bootstrapped path coefficients: t-values, 95% CI

```{r}
boot_pls <- bootstrap_model(pls, nboot=1000)
```

```{r}
summary(boot_pls)
```


# Question 2

## a. Create a common factor model using SEMinR

### i. Respecify all the constructs using reflective() function

```{r}
cfm_mm <- constructs(
  reflective('TRUST', multi_items('TRST', 1:4)),
  reflective('SEC', multi_items('PSEC', 1:4)),
  reflective('REP', multi_items('PREP', 1:4)),
  reflective('INV', multi_items('PINV', 1:3)),
  reflective('POL', multi_items('PPSS', 1:3)),
  reflective('FAML', single_item('FAML1')),
  interaction_term(iv='REP', moderator='POL', method=orthogonal)
)
```

### ii. Use the same structural model as before

```{r}
cfm_sm <- relationships(
  paths(from = c("REP","INV","POL","FAML","REP*POL"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
)
```

## b. Show the result

```{r}
cfm_pls <- estimate_cbsem(
  data = sec,
  measurement_model = cfm_mm,
  structural_model = cfm_sm
)

cfm_pls_report <- summary(cfm_pls)
cfm_pls_report
```


### i. Plot the model

```{r}
plot(cfm_pls, title="Common-Factor Models using CB-SEM")
```

### ii. Loadings of composites

```{r}
cfm_pls_report$loadings
```

### iii. Regression coefficients and P-values

```{r}
cfm_pls_report$paths
```