---
title: "BACS HW12"
author: "Bijon Setyawan Raya"
date: "5/12/2021"
output: pdf_document
---

```{r, include=FALSE}
library(ISLR)
```

```{r}
cars <- Auto
head(cars)
```

# Question 1

```{r}
cars_log <- with(cars, data.frame(log(mpg), log(cylinders), log(displacement),
log(horsepower), log(weight), log(acceleration), year, origin))

names(cars_log) <- names(cars)[1:8] # rename the columns
head(cars_log)
```

## a. Run a new regression on the cars_log dataset, with mpg.log. dependent on all other variables

```{r}
cars_regr <- 
  lm(
    mpg ~ 
      cylinders + 
      displacement + 
      horsepower + 
      weight + 
      acceleration + 
      year + 
      factor(origin), 
    data = cars_log
  )
summary(cars_regr)
```

### i. Which log-transformed factors have a significant effect on log.mpg. at 10% significance?

`horsepower`, `weight`, `acceleration`, `year`, `factor(origin)2`, and `factor(origin)3`.

### ii. Do some new factors now have effects on mpg, and why might this be?

`acceleration` and `horsepower` suddenly became significant in this case, which they weren't in the previous homework.

### iii. Which factors still have insignificant or opposite (from correlation) effects on mpg? Why might this be?

Only `cylinders`. The more cylinders cars have, the higher the gas consumption.

## b. Let’s take a closer look at weight, because it seems to be a major explanation of mpg

### i. Create a regression (call it regr_wt) of mpg on weight from the original cars dataset

```{r}
regr_wt <- lm(mpg ~ weight, data = Auto)
```

### ii. Create a regression (call it regr_wt_log) of log.mpg. on log.weight. from cars_log

```{r}
regr_wt_log <- lm(mpg ~ weight, data = cars_log)
```

### iii. visualize the residuals of both regression models

1. density plots of residuals
```{r}
plot(
  density(resid(regr_wt)), 
  main = "Residual Distribution MPG ~ Weight", 
  lwd = 2, 
  col = "red", 
  xlab = "Residual"
)
```

```{r}
plot(
  density(resid(regr_wt_log)), 
  main = "Residual Distribution MPG ~ Weight (log)", 
  lwd = 2, 
  col = "blue", 
  xlab = "Residual (log)"
)
```

2. scatterplot of log.weight. vs. residuals

```{r}
library(ggplot2)
ggplot(
  cars_log, 
  aes(
    x = weight, 
    y = lm(mpg ~ weight)$residual)
  ) +
  geom_point() +
  xlab("Weight (log)") +
  ylab("MPG ~ Weight Residual (log)")
```

## c. Let’s examine the 95% confidence interval of the slope of log.weight. vs. log.mpg.

```{r}
boot_intercept <- function(dataset) {
  # pick data points' indexes
  random_samples <- sample(1:nrow(dataset), replace = TRUE)
  
  slopes <- lm(mpg ~ weight, data = dataset[random_samples,])
  abline(slopes, lwd = 1, col="grey")
  return(slopes$coefficients)
}
```


```{r}
plot(
  cars_log$weight, 
  cars_log$mpg, 
  col = "steelblue", 
  pch = 19, 
  xlab = "mpg (log)",
  ylab = "weight (log)",
  main = "95% CI of Intercept Value of MPG ~ Weight"
)

regression_coeffs <- replicate(500, boot_intercept(cars_log))
abline(a = mean(regression_coeffs["(Intercept)",]), b = mean(regression_coeffs["weight",]))
```

```{r}
mpg_weight_regr <- lm(mpg ~ weight, data = cars_log)
mpg_weight_regr
```

```{r}
t.test(regression_coeffs["(Intercept)",], mu = 11.515)
```

