---
title: "BACS HW2"
author: "Bijon Setyawan Raya 109062710"
date: "3/14/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(cowplot)
```

# Question 1

## (a) A graph with negatively skewed tail
```{r}
d1 <- rnorm(n=500, mean=45, sd=1)
d2 <- rnorm(n=200, mean=30, sd=2)
d3 <- rnorm(n=100, mean=15, sd=3)

dataset <- c(d1, d2, d3)
plot(density(dataset), col="blue", lwd=2, main="Distribution 2")

abline(v=mean(dataset))
abline(v=median(dataset), lty="dashed")
```

## (b) A graph with bell shaped curve
```{r}
dataset <- c(rnorm(n=800, mean=25,sd=5))

plot(density(dataset), col="blue", main="Distribution 3")

abline(v=mean(dataset))
abline(v=median(dataset), lty="dashed")
```

## (c) Which of the central measurements is more likely to be affeccted by outliers in the data? Is it Mean or Median?
Mean will more likely to be affected by outliers in the data.
Mean will increase because of the existence of higher outliers. Conversely, Mean will decrease because of the existence of lower outliers.

# Question 2
## (a)
```{r}
rdata <- rnorm(n=2000, mean=0, sd=1)

dataset <- c(rdata)

plot(density(rdata), col="blue", main="Random Data")

abline(v=mean(dataset))
abline(v=median(dataset), col="red", lty="dashed")

# negative STDs
abline(v=sd(dataset) * -1, col="red", lty="dashed")
abline(v=sd(dataset) * -2, col="red", lty="dashed")
abline(v=sd(dataset) * -3, col="red", lty="dashed")

# positive STDs
abline(v=sd(dataset), col="red", lty="dashed")
abline(v=sd(dataset) * 2, col="red", lty="dashed")
abline(v=sd(dataset) * 3, col="red", lty="dashed")
```

## (b)
```{r}
rdata <- rnorm(n=2000, mean=0, sd=1)

dataset <- c(rdata)

plot(density(rdata), col="blue", main="Random Data")

abline(v=mean(dataset))
abline(v=median(dataset), col="red", lty="dashed")

two_b_quantiles = quantile(dataset)

abline(v=two_b_quantiles[2])
abline(v=two_b_quantiles[3])
abline(v=two_b_quantiles[4])

# negative STDs
abline(v=sd(dataset) * -1, col="red", lty="dashed")
abline(v=sd(dataset) * -2, col="red", lty="dashed")
abline(v=sd(dataset) * -3, col="red", lty="dashed")

# positive STDs
abline(v=sd(dataset), col="red", lty="dashed")
abline(v=sd(dataset) * 2, col="red", lty="dashed")
abline(v=sd(dataset) * 3, col="red", lty="dashed")
```
```{r}
rdata <- rnorm(n=2000, mean=0, sd=1)

dataset <- c(rdata)

q1 <- quantile(rdata, 0.25)
q1
```

As we can see in the graph above, we can see that:
* 1st quartile is `-0.6461` STD away from the mean
* 2nd quartile is `-0.0003` STD away from the mean
* 3nd quartile is `0.6694` STD away fromt the mean

# Question 3
```{r}
random_dataset <- rnorm(n=2000, mean=35, sd=3.5)

two_c_dataset <- c(random_dataset)

plot(density(two_c_dataset), col="blue", main="2C Graph")

# negative STDs
abline(v=sd(random_dataset) * -1, col="red", lty="dashed")
abline(v=sd(random_dataset) * -2, col="red", lty="dashed")
abline(v=sd(random_dataset) * -3, col="red", lty="dashed")

# positive STDs
abline(v=sd(random_dataset), col="red", lty="dashed")
abline(v=sd(random_dataset) * 2, col="red", lty="dashed")
abline(v=sd(random_dataset) * 3, col="red", lty="dashed")
```

```{r}
sd(two_c_dataset)
```