---
title: "BACS HW2"
author: "109062710"
date: "March 17, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
library(ggplot2)
library(glue)
library(gridExtra)
library(readr)
```

# Question 1

Here is the helper functions for Q1
```{r}
standardize <- function(data) {
  standardized <- (data - mean(data)) / sd(data)
  return(standardized)
}

create_density <- function(data, title) {
  mean <- mean(data)
  ggplot(mapping = aes(data)) +
    geom_density(
      fill="#69b3a2", 
      color="#e9ecef",
    ) +
    geom_vline(xintercept = mean, col="black") + 
    geom_vline(xintercept = c(sd(data) * -1, sd(data)), col="red") +
    ggtitle(title)
}

create_histogram <- function(data, title) {
  n = length(data)
  
  # Freidman-Darconis' Binwidth Rule
  binwidth <- (2 * IQR(data)) / n^(1/3)
  bins <- ceiling(max(data) - min(data)) + binwidth
  
  ggplot(mapping = aes(data)) +
    geom_histogram(
      fill="#69b3a2", 
      color="#e9ecef",
      bins = bins,
      binwidth = binwidth
    ) +
    ggtitle(title)
}
```

## A. create a normal distribution `(mean = 940, sd = 190)` and standardize it
```{r}
rnorm <- rnorm(1000, mean = 940, sd = 190)
rnorm_std <- standardize(rnorm)
```


### i) What should we expect the mean and standard deviation of rnorm_std to be, and why?
```{r, include = FALSE}
nonstd_rnorm_mean <- mean(rnorm)
nonstd_rnorm_sd <- sd(rnorm)

std_rnorm_mean <- mean(rnorm_std)
std_rnorm_sd <- sd(rnorm_std)
```

```{r}
glue(
  "The mean of rnorm is {nonstd_rnorm_mean}, 
  and its standard deviation is {nonstd_rnorm_sd}."
)

glue(
  "The mean of rnorm_std is {std_rnorm_mean}, 
  and its standard deviation is {std_rnorm_sd}."
)
```

```{r, include=FALSE}
std_rnorm_hist <- 
  create_histogram(
    rnorm_std, 
    "Standardized ND Histogram"
  )

std_rnorm_density <- 
  create_density(
    rnorm_std, 
    "Standardized ND Density"
  )
```

```{r}
grid.arrange(
  std_rnorm_hist, 
  std_rnorm_density, 
  ncol=1, 
  nrow=2
)
```
As we can see from the result above and the graph above, mean value and standard deviation value are concentrated around `-3` to `3`, instead of `0` to `1600` which before standardization. After standardization, each `x_value` in the graph represents how far each instance from the mean in STD unit. This happens because standardization scales down everything to STD unit scale.

### ii) What should the distribution (shape) of rnorm_std look like, and why?
```{r, include=FALSE}
nonstd_rnorm_hist <- create_histogram(
    rnorm, 
    "Non-STD ND Histogram"
  )

nonstd_rnorm_density <- 
  create_density(
    rnorm, 
    "Non-STD ND Density"
  )
```

```{r}
grid.arrange(
  nonstd_rnorm_hist, 
  nonstd_rnorm_density, 
  std_rnorm_hist, 
  std_rnorm_density, 
  ncol=2, 
  nrow=2
)
```
Basically, `rnorm_std` plots should look entirely the same compared to `rnorm` plots. Let's take the graph above as our main reference.
However, there are two key points worth mentioning here:
1. Non-standardized and standardized histograms look almost the same, but there is a slight difference if you take a close look. 
2. The Standard Deviation lines are located in unusual location in non-standardized histogram. Unlike in standardized histogram plot, the SD lines are located at the expected locations.

### iii)  What do we generally call distributions that are normal and standardized?
It's called **bell-shaped curved** distribution.

## B. Create a standardized version of `minday` from the earlier question (let’s call it `minday_std`)

```{r, include = FALSE}
dataset <- read_csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw3/first_bookings_datetime_sample.txt")
hours  <- as.POSIXlt(dataset$datetime, format="%m/%d/%Y %H:%M")$hour
mins   <- as.POSIXlt(dataset$datetime, format="%m/%d/%Y %H:%M")$min
minday <- hours*60 + mins
```

```{r}
minday_std <- standardize(minday)
```

### i) What should we expect the mean and standard deviation of `minday_std` to be, and why?
```{r, include=FALSE}
minday_std_mean <- mean(minday_std)
minday_std_sd <- sd(minday_std)
```

```{r}
glue("The mean of minday_std {minday_std_mean}, while its SD is {minday_std_sd}.")
```
we expect the mean and the STD values to be really small which are within `-2.5` to `2.5` range after standardization. This happens because standardization scales down everything to STD unit scale.

### ii) What should the distribution of `minday_std` look like compared to `minday`, and why?
Before standardization,
```{r, include = FALSE}
minday_hist <- 
  create_histogram(
    minday, 
    "Minute (of the day) of first ever booking"
  )

minday_density <- 
  create_density(
    minday, 
    "Minute (of the day) of first ever booking"
  )
```

```{r}
grid.arrange(
  minday_hist, 
  minday_density, 
  ncol=1, 
  nrow=2
)
```

After standardization,
```{r, include=FALSE}
minday_std_hist <- 
  create_histogram(
    minday_std, 
    "Minute (of the day) of first ever booking"
  )

minday_std_density <- 
  create_density(
    minday_std, 
    "Minute (of the day) of first ever booking"
  )
```

```{r}
grid.arrange(
  minday_std_hist, 
  minday_std_density, 
  ncol=1, 
  nrow=2
)
```
The situation is the similar to the section a, part ii. In the non-standardized data set, the STD lines are far away when we expect them to be. Besides, we have a huge range of `x_value` which is from `0` to `1500`.

However, in the standardized data set, the mean line is exactly in between the STD lines. In addition, we have a smaller range of `x_value` which is from `-4` to `4`.

# Question 2

# Question 3