---
title: "BACS HW3"
author: "109062710"
date: "March 17, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
library(ggplot2)
library(glue)
library(gridExtra)
library(readr)
```

# Question 1

Here is the helper functions for Q1
```{r}
standardize <- function(data) {
  standardized <- (data - mean(data)) / sd(data)
  return(standardized)
}

create_density <- function(data, title) {
  mean <- mean(data)
  
  sd_values = c(
    mean(data) - 2 * sd(data), 
    mean(data) - sd(data), 
    mean(data) + sd(data), 
    mean(data) + 2 * sd(data)
  )
  
  ggplot(mapping = aes(data)) +
    geom_density(
      fill="#69b3a2", 
      color="#e9ecef",
    ) +
    geom_vline(xintercept = mean, col="black") + 
    geom_vline(xintercept = sd_values, col="red") +
    ggtitle(title)
}

create_histogram <- function(data, title) {
  n = length(data)
  
  # Freidman-Darconis' BiUnwidth Rule
  binwidth <- (2 * IQR(data)) / n^(1/3)
  bins <- ceiling(max(data) - min(data)) + binwidth
  
  ggplot(mapping = aes(data)) +
    geom_histogram(
      fill="#69b3a2", 
      color="#e9ecef",
      bins = bins,
      binwidth = binwidth
    ) +
    ggtitle(title)
}
```

## A. create a normal distribution `(mean = 940, sd = 190)` and standardize it
```{r}
rnorm <- rnorm(1000, mean = 940, sd = 190)
rnorm_std <- standardize(rnorm)
```

### i) What should we expect the mean and standard deviation of rnorm_std to be, and why?
```{r, include = FALSE}
nonstd_rnorm_mean <- mean(rnorm)
nonstd_rnorm_sd <- sd(rnorm)

std_rnorm_mean <- mean(rnorm_std)
std_rnorm_sd <- sd(rnorm_std)
```

```{r}
glue(
  "The mean of rnorm is {nonstd_rnorm_mean}, 
  and its standard deviation is {nonstd_rnorm_sd}."
)

glue(
  "The mean of rnorm_std is {std_rnorm_mean}, 
  and its standard deviation is {std_rnorm_sd}."
)
```

```{r, include=FALSE}
rnorm_density <- 
  create_density(
    rnorm, 
    "Non-STD Density"
  )

rnorm_std_density <- 
  create_density(
    rnorm_std, 
    "STD Density"
  )
```

```{r}
grid.arrange(
  rnorm_density, 
  rnorm_std_density, 
  ncol=1, 
  nrow=2
)
```
As we can see from the result above and the graph above, mean value and standard deviation value are concentrated around `-3` to `3`, instead of `0` to `1600` which before standardization. After standardization, each `x_value` in the graph represents how far each instance from the mean in STD unit. This happens because standardization scales down everything to STD unit scale.

### ii) What should the distribution (shape) of rnorm_std look like, and why?
```{r, include=FALSE}
rnorm_hist <- 
  create_histogram(
    rnorm, 
    "Non-STD ND Histogram"
  )

rnorm_std_hist <- 
  create_histogram(
    rnorm_std, 
    "STD ND Density"
  )
```

```{r}
grid.arrange(
  rnorm_hist, 
  rnorm_density, 
  rnorm_std_hist, 
  rnorm_std_density, 
  ncol=2, 
  nrow=2
)
```
Basically, `rnorm_std` and `rnorm` plots should look entirely the same, but they are not. Let's take the graph above as a reference.

However, there is a worth mentioning here:

1. Non-standardized and standardized histograms look almost the same, but there is a slight difference if you take a close look. 

2. The `x_values` range becomes smaller in standardized density plot because standardization scales down everything to STD unit scale.

### iii)  What do we generally call distributions that are normal and standardized?
It's called **bell-shaped curved** distribution.

## B. Create a standardized version of `minday` from the earlier question (let’s call it `minday_std`)

```{r, include = FALSE}
dataset <- read_csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw3/first_bookings_datetime_sample.txt")
hours  <- as.POSIXlt(dataset$datetime, format="%m/%d/%Y %H:%M")$hour
mins   <- as.POSIXlt(dataset$datetime, format="%m/%d/%Y %H:%M")$min
minday <- hours*60 + mins
```

```{r}
minday_std <- standardize(minday)
```

### i) What should we expect the mean and standard deviation of `minday_std` to be, and why?
```{r, include=FALSE}
minday_std_mean <- mean(minday_std)
minday_std_sd <- sd(minday_std)
```

```{r}
glue("The mean of minday_std {minday_std_mean}, while its SD is {minday_std_sd}.")
```
We expect the mean and the STD values to be really small which are within `-2.5` to `2.5` range after standardization because standardization scales down everything to STD unit scale.

### ii) What should the distribution of `minday_std` look like compared to `minday`, and why?
Before standardization,
```{r, include = FALSE}
minday_hist <- 
  create_histogram(
    minday, 
    "Minute (of the day) of first ever booking"
  )

minday_density <- 
  create_density(
    minday, 
    "Minute (of the day) of first ever booking"
  )
```

```{r}
grid.arrange(
  minday_hist, 
  minday_density, 
  ncol=1, 
  nrow=2
)
```

After standardization,
```{r, include=FALSE}
minday_std_hist <- 
  create_histogram(
    minday_std, 
    "Minute (of the day) of first ever booking"
  )

minday_std_density <- 
  create_density(
    minday_std, 
    "Minute (of the day) of first ever booking"
  )
```

```{r}
grid.arrange(
  minday_std_hist, 
  minday_std_density, 
  ncol=1, 
  nrow=2
)
```
The situation is the similar to the section a, part ii. In the non-standardized data set, the STD lines are far away when we expect them to be. Besides, we have a huge range of `x_value` which is from `0` to `1500`.

However, in the standardized data set, the mean line is exactly in between the STD lines. In addition, we have a smaller range of `x_value` which is from `-4` to `4`.

# Question 2
```{r}
visualize_sample_ci <- function(num_samples = 100, sample_size = 100, 
                                pop_size=10000, distr_func=rnorm, ...) {
  # Simulate a large population
  population_data <- distr_func(pop_size, ...)
  pop_mean <- mean(population_data)
  pop_sd <- sd(population_data)
  
  # Simulate samples
  samples <- replicate(num_samples, 
                       sample(population_data, sample_size, replace=FALSE))
  
  # Calculate descriptives of samples
  sample_means = apply(samples, 2, FUN=mean)
  sample_stdevs = apply(samples, 2, FUN=sd)
  sample_stderrs <- sample_stdevs/sqrt(sample_size)
  ci95_low  <- sample_means - sample_stderrs*1.96
  ci95_high <- sample_means + sample_stderrs*1.96 
  ci99_low  <- sample_means - sample_stderrs*2.58
  ci99_high <- sample_means + sample_stderrs*2.58
  
  # Visualize confidence intervals of all samples
  plot(NULL, xlim=c(pop_mean-(pop_sd/2), pop_mean+(pop_sd/2)), 
       ylim=c(1,num_samples), ylab="Samples", xlab="Confidence Intervals")
  add_ci_segment(ci95_low, ci95_high, ci99_low, ci99_high,
                 sample_means, 1:num_samples, good=TRUE)
  
  # Visualize samples with CIs that don't include population mean
  bad = which(((ci95_low > pop_mean) | (ci95_high < pop_mean)) |
              ((ci99_low > pop_mean) | (ci99_high < pop_mean)))
  add_ci_segment(ci95_low[bad], ci95_high[bad], ci99_low[bad], ci99_high[bad],
                 sample_means[bad], bad, good=FALSE)
  
  # Draw true population mean
  abline(v=mean(population_data))
}

add_ci_segment <- function(ci95_low, ci95_high, ci99_low, ci99_high, 
                           sample_means, indices, good=TRUE) {
  segment_colors <- list(c("lightcoral", "coral3", "coral4"),
                         c("lightskyblue", "skyblue3", "skyblue4"))
  color <- segment_colors[[as.integer(good)+1]]
  
  segments(ci99_low, indices, ci99_high, indices, lwd=3, col=color[1])
  segments(ci95_low, indices, ci95_high, indices, lwd=3, col=color[2])
  points(sample_means, indices, pch=18, cex=0.6, col=color[3])
}

visualize_sample_ci(sample_size=300, distr_func=runif, min=17, max=35)
```

# Question 3