---
title: "BACS HW3"
author: "109062710"
date: "March 17, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
library(ggplot2)
library(glue)
library(gridExtra)
library(readr)
```

# Question 1

Here is the helper functions for Q1
```{r}
standardize <- function(data) {
  standardized <- (data - mean(data)) / sd(data)
  return(standardized)
}

create_density <- function(data, title) {
  mean <- mean(data)
  
  sd_values = c(
    mean(data) - 2 * sd(data), 
    mean(data) - sd(data), 
    mean(data) + sd(data), 
    mean(data) + 2 * sd(data)
  )
  
  ggplot(mapping = aes(data)) +
    geom_density(
      fill="#69b3a2", 
      color="#e9ecef",
    ) +
    geom_vline(xintercept = mean, col="black") + 
    geom_vline(xintercept = sd_values, col="red") +
    ggtitle(title)
}

create_histogram <- function(data, title) {
  n = length(data)
  
  # Freidman-Darconis' BiUnwidth Rule
  binwidth <- (2 * IQR(data)) / n^(1/3)
  bins <- ceiling(max(data) - min(data)) + binwidth
  
  ggplot(mapping = aes(data)) +
    geom_histogram(
      fill="#69b3a2", 
      color="#e9ecef",
      bins = bins,
      binwidth = binwidth
    ) +
    ggtitle(title)
}
```

## A. create a normal distribution `(mean = 940, sd = 190)` and standardize it
```{r}
rnorm_q1 <- rnorm(1000, mean = 940, sd = 190)
rnorm_std <- standardize(rnorm_q1)
```

### i) What should we expect the mean and standard deviation of rnorm_std to be, and why?
```{r, include = FALSE}
nonstd_rnorm_mean <- mean(rnorm_q1)
nonstd_rnorm_sd <- sd(rnorm_q1)

std_rnorm_mean <- mean(rnorm_std)
std_rnorm_sd <- sd(rnorm_std)
```

```{r, echo=FALSE}
glue(
  "The mean of rnorm is {nonstd_rnorm_mean}, 
  and its standard deviation is {nonstd_rnorm_sd}."
)

glue(
  "The mean of rnorm_std is {std_rnorm_mean}, 
  and its standard deviation is {std_rnorm_sd}."
)
```

```{r, include=FALSE}
rnorm_density <- 
  create_density(
    rnorm_q1, 
    "Non-STD Density"
  )

rnorm_std_density <- 
  create_density(
    rnorm_std, 
    "STD Density"
  )
```

```{r}
grid.arrange(
  rnorm_density, 
  rnorm_std_density, 
  ncol=1, 
  nrow=2
)
```
In this case, the `mean` value is `0`. After standardization, `x_value` has a range of `-3` to `3`. That range represents how far each instance from the mean in STD unit. This happens because standardization scales down everything to STD unit scale.

### ii) What should the distribution (shape) of rnorm_std look like, and why?
```{r, include=FALSE}
rnorm_hist <- 
  create_histogram(
    rnorm_q1, 
    "Non-STD ND Histogram"
  )

rnorm_std_hist <- 
  create_histogram(
    rnorm_std, 
    "STD ND Density"
  )
```

```{r}
grid.arrange(
  rnorm_hist, 
  rnorm_density, 
  rnorm_std_hist, 
  rnorm_std_density, 
  ncol=2, 
  nrow=2
)
```
Basically, `rnorm_std` and `rnorm` plots should look entirely the same, but they are not. Let's take the graph above as a reference.

However, there is a worth mentioning here:

1. Non-standardized and standardized histograms look almost the same, but there is a slight difference if you take a close look. 

2. The `x_values` range becomes smaller in standardized density plot because standardization scales down everything to STD unit scale.

### iii)  What do we generally call distributions that are normal and standardized?
It's called **bell-shaped curved** distribution.

## B. Create a standardized version of `minday` from the earlier question (let’s call it `minday_std`)

```{r, include = FALSE}
# dataset <- read_csv("/home/johnbjohn/Documents/git_repos/bacs-hw/hw3/first_bookings_datetime_sample.txt")
dataset <- read_csv("/Users/bijonsetyawan/Documents/Git/bacs-hw/hw3/first_bookings_datetime_sample.txt")
hours  <- as.POSIXlt(dataset$datetime, format="%m/%d/%Y %H:%M")$hour
mins   <- as.POSIXlt(dataset$datetime, format="%m/%d/%Y %H:%M")$min
minday <- hours*60 + mins
```

```{r}
minday_std <- standardize(minday)
```

### i) What should we expect the mean and standard deviation of `minday_std` to be, and why?
```{r, include=FALSE}
minday_std_mean <- mean(minday_std)
minday_std_sd <- sd(minday_std)
```

```{r, echo=FALSE}
glue("The mean of minday_std {minday_std_mean}, while its SD is {minday_std_sd}.")
```
We expect the mean and the STD values to be really small which are within `-2.5` to `2.5` range after standardization because standardization scales down everything to STD unit scale. In this case, `mean` becomes zero.

### ii) What should the distribution of `minday_std` look like compared to `minday`, and why?
Before standardization,
```{r, include = FALSE}
minday_hist <- 
  create_histogram(
    minday, 
    "Minute (of the day) of first ever booking"
  )

minday_density <- 
  create_density(
    minday, 
    "Minute (of the day) of first ever booking"
  )
```

```{r}
grid.arrange(
  minday_hist, 
  minday_density, 
  ncol=1, 
  nrow=2
)
```

After standardization,
```{r, include=FALSE}
minday_std_hist <- 
  create_histogram(
    minday_std, 
    "Minute (of the day) of first ever booking"
  )

minday_std_density <- 
  create_density(
    minday_std, 
    "Minute (of the day) of first ever booking"
  )
```

```{r}
grid.arrange(
  minday_std_hist, 
  minday_std_density, 
  ncol=1, 
  nrow=2
)
```
The situation is the similar to the section a, part ii. In the non-standardized data set, the STD lines are far away when we expect them to be. Besides, we have a huge range of `x_value` which is from `0` to `1500`.

However, in the standardized data set, the mean line is exactly in between the STD lines. In addition, we have a smaller range of `x_value` which is from `-4` to `4`.

# Question 2
```{r, include = FALSE}
visualize_sample_ci <- function(
  num_samples = 100, 
  sample_size = 100, 
  pop_size=10000, 
  title, 
  distr_func=rnorm, ...) {
  # Simulate a large population
  population_data <- distr_func(pop_size, ...)
  pop_mean <- mean(population_data)
  pop_sd <- sd(population_data)
  
  # Simulate samples
  samples <- replicate(
    num_samples, 
    sample(
      population_data, 
      sample_size, 
      replace=FALSE
    )
  )
  
  # Calculate descriptives of samples
  sample_means = apply(samples, 2, FUN=mean)
  sample_stdevs = apply(samples, 2, FUN=sd)
  sample_stderrs <- sample_stdevs/sqrt(sample_size)
  ci95_low  <- sample_means - sample_stderrs * 1.96
  ci95_high <- sample_means + sample_stderrs * 1.96 
  ci99_low  <- sample_means - sample_stderrs * 2.58
  ci99_high <- sample_means + sample_stderrs * 2.58
  
  # Visualize confidence intervals of all samples
  plot(
    NULL, 
    xlim=c(pop_mean-(pop_sd/2), pop_mean+(pop_sd/2)), 
    ylim=c(1,num_samples), 
    ylab="Samples", 
    xlab="Confidence Intervals", 
    main=title
  )
  
  add_ci_segment(
    ci95_low, 
    ci95_high, 
    ci99_low, 
    ci99_high,
    sample_means, 
    1:num_samples, 
    good=TRUE
  )
  
  # Visualize samples with CIs that don't include population mean
  bad = which(
    ((ci95_low > pop_mean) | (ci95_high < pop_mean)) |
    ((ci99_low > pop_mean) | (ci99_high < pop_mean))
  )
  
  add_ci_segment(
    ci95_low[bad], 
    ci95_high[bad], 
    ci99_low[bad], 
    ci99_high[bad],
    sample_means[bad], 
    bad, 
    good=FALSE
  )
  
  # Draw true population mean
  abline(v=mean(population_data))
}

add_ci_segment <- function(
  ci95_low, 
  ci95_high, 
  ci99_low, 
  ci99_high, 
  sample_means, indices, good=TRUE) {
  segment_colors <- list(
    c("lightcoral", "coral3", "coral4"),
    c("lightskyblue", "skyblue3", "skyblue4")
  )
  
  color <- segment_colors[[as.integer(good)+1]]
  
  segments(
    ci99_low, 
    indices, 
    ci99_high, 
    indices, 
    lwd=3,
    col=color[1]
  )
  
  segments(
    ci95_low, 
    indices, 
    ci95_high, 
    indices, 
    lwd=3, 
    col=color[2]
  )
  
  points(
    sample_means, 
    indices, 
    pch=18, 
    cex=0.6, 
    col=color[3]
  )
}

ci_95 <- function(
  num_samples = 100, 
  sample_size = 100, 
  pop_size=10000, 
  distr_func=rnorm, ...) {
  # Simulate a large population
  population_data <- distr_func(pop_size, ...)
  pop_mean <- mean(population_data)
  pop_sd <- sd(population_data)
  
  # Simulate samples
  samples <- replicate(
    num_samples, 
    sample(
      population_data, 
      sample_size, 
      replace=FALSE)
  )
  
  # Calculate descriptives of samples
  sample_means = apply(samples, 2, FUN=mean)
  sample_stdevs = apply(samples, 2, FUN=sd)
  sample_stderrs <- sample_stdevs/sqrt(sample_size)
  ci95_low  <- sample_means - sample_stderrs*1.96
  ci95_high <- sample_means + sample_stderrs*1.96 
  
  # Visualize samples with CIs that don't include population mean
  result = which(((ci95_low > pop_mean) | (ci95_high < pop_mean)))
  return(result)
}

ci_99 <- function(
  num_samples = 100, 
  sample_size = 100, 
  pop_size=10000, 
  distr_func=rnorm, ...) {
  # Simulate a large population
  population_data <- distr_func(pop_size, ...)
  pop_mean <- mean(population_data)
  pop_sd <- sd(population_data)
  
  # Simulate samples
  samples <- replicate(
    num_samples, 
    sample(
      population_data, 
      sample_size, 
      replace=FALSE)
  )
  
  # Calculate descriptives of samples
  sample_means = apply(samples, 2, FUN=mean)
  sample_stdevs = apply(samples, 2, FUN=sd)
  sample_stderrs <- sample_stdevs/sqrt(sample_size)
  ci99_low  <- sample_means - sample_stderrs*2.58
  ci99_high <- sample_means + sample_stderrs*2.58
  
  # Visualize samples with CIs that don't include population mean
  result = which(((ci99_low > pop_mean) | (ci99_high < pop_mean)))
  
  return(result)
}
```

## a) Simulate 100 samples (each of size 100), from a normally distributed population of 10,000:
### i) How many samples do we expect to NOT include the population mean in its 95% CI?
```{r, echo=FALSE}
ci95 <- c()
for (i in 1:200){
  ci95[i] <- length(
    ci_95(
      num_samples = 100, 
      sample_size = 100, 
      pop_size=10000, 
      distr_func=rnorm, 
      mean=20, 
      sd=3
    )
  )
}

#Use mean as estimator
cat (mean(ci95),"\n")
```
Out of 100 simulations, the answer can be rounded down to 5 samples.

### ii) How many samples do we expect to NOT include the population mean in their 99% CI?
```{r, echo=FALSE}
ci99 <- c()
for (i in 1:200){
  ci99[i] <- length(
    ci_99(
      num_samples = 100, 
      sample_size = 100, 
      pop_size=10000, 
      distr_func=rnorm, 
      mean=20, 
      sd=3
    )
  )
}

glue(mean(ci99))
```
Out of 100 simulations, the answer can be rounded down to 1 sample.

## b) Rerun the previous simulation with larger samples (sample_size=300):
### i) Now that the size of each sample has increased, do we expect their 95% and 99% CI to become wider or narrower than before?

```{r, echo=FALSE}
visualize_sample_ci(
  num_samples = 100, 
  sample_size = 100, 
  pop_size=10000, 
  distr_func=rnorm, 
  mean=20, 
  sd=3, 
  title="Sample Size = 100"
)

visualize_sample_ci(
  num_samples = 100, 
  sample_size = 300, 
  pop_size=10000, 
  distr_func=rnorm, 
  mean=20, 
  sd=3, 
  title="Sample Size = 300"
)
```

As we can see from those two plots above, the 95% and 99% CI become narrower when the sample size increases.

### ii) This time, how many samples (out of the 100) would we expect to NOT include the population mean in its 95% CI?
```{r, echo=FALSE}
ci95 <- c()
for (i in 1:200){
  ci95[i] <- length(
    ci_95(
      num_samples = 100,
      sample_size = 300, 
      pop_size=10000, 
      distr_func=rnorm, 
      mean=20, 
      sd=3
    )
  )
}

#Use mean as estimator
glue(mean(ci95))
```
Out of 100 simulations, the answer can be rounded down to 4 samples.

## c) If we ran the above two examples (a and b) using a uniformly distributed population (specify distr_func=runif for visualize_sample_ci), how do you expect your answers to (a) and (b) to change, and why?

### `num_sample = 100` & `distr_func = runif`
i) How many samples do we expect to NOT include the population mean in their 95% CI? 
```{r, echo=FALSE}
ci95 <- c()
for (i in 1:200){
  ci95[i] <- length(
    ci_95(
      num_samples = 100,
      sample_size = 100, 
      pop_size = 10000, 
      distr_func = runif
    )
  )
}

#Use mean as estimator
glue(mean(ci95))
```

ii) How many samples do we expect to NOT include the population mean in their 99% CI? 
```{r, echo=FALSE}
ci99 <- c()
for (i in 1:200){
  ci99[i] <- length(
    ci_99(
      num_samples = 100,
      sample_size = 100, 
      pop_size=10000, 
      distr_func=runif
    )
  )
}

#Use mean as estimator
glue(mean(ci99))
```

### `num_sample = 300` & `distr_func = runif`
i) How many samples do we expect to NOT include the population mean in their 95% CI? 
```{r, echo=FALSE}
ci95 <- c()
for (i in 1:200){
  ci95[i] <- length(
    ci_95(
      num_samples = 100,
      sample_size = 300, 
      pop_size = 10000, 
      distr_func = runif
    )
  )
}

#Use mean as estimator
glue(mean(ci95))
```

ii) How many samples do we expect to NOT include the population mean in their 99% CI? 
```{r, echo=FALSE}
ci99 <- c()
for (i in 1:200){
  ci99[i] <- length(
    ci_99(
      num_samples = 100,
      sample_size = 300, 
      pop_size=10000, 
      distr_func=runif
    )
  )
}

#Use mean as estimator
glue(mean(ci99))
```

When we look at those two configurations above, we can see that the changes in mean and standard deviation values both in `rnorm` and `runif` follow the same pattern.

```{r, echo=FALSE}
visualize_sample_ci(
  num_samples = 100, 
  sample_size = 100, 
  pop_size = 10000, 
  distr_func = runif,
  title = "Sample Size = 100"
)

visualize_sample_ci(
  num_samples = 100, 
  sample_size = 300,
  pop_size=10000, 
  distr_func=runif, 
  title="Sample Size = 300"
)
```
However,we can see that the the 95% and 99% CI are concentrated in `0.35 - 0.65` range. Conversely, they are concentrated in `18.5 - 21.5` range. Clearly, the `x_value` range has been reduced in `distr_func = runif`.

# Question 3
## a) What is the “average” booking time for new members making their first restaurant booking?

### i) Use traditional statistical methods to estimate the population mean of minday, its standard error, and the 95% confidence interval (CI) of the sampling means
```{r}
mean <- mean(minday)
sd_error <- sd(minday) / ( length(minday)^0.5 )
ci95_low <- mean - 1.96 * sd_error
ci95_high <- mean + 1.96 * sd_error
```

The mean value is
```{r, echo=FALSE}
glue(mean)
```

The standard deviation error is
```{r, echo=FALSE}
glue(sd_error)
```

The 95% CI is between
```{r, echo=FALSE}
glue("{ci95_low} & {ci95_high}")
```

### ii) Bootstrap to produce 2000 new samples from the original sample
```{r}
bootstrapped_samples <- replicate(2000, sample(minday, 10000, replace=TRUE))
```

### iii) Visualize the means of the 2000 bootstrapped samples
```{r, echo=FALSE}
plot(
  density(minday), 
  lwd=1, 
  main="Population & Bootstrapped Samples"
)

plot_sample <- function(sample) {
  lines(
    density(sample), 
    col="#8cd9db"
  )
    
  return(
    mean(sample)
  )
}

sample_means <- apply(bootstrapped_samples, 2, FUN=plot_sample)

lines(density(minday), col="red", lwd=2, lty="dashed")

legend(
  "topleft", 
  legend=c("Bootstrapped", "Population"), 
  col=c("#8cd9db", "red"), 
  lty = c("solid", "dashed"), 
  bty = "n", 
  pt.cex = 2, 
  cex = 1.2, 
  text.col = "black", 
  horiz = F 
)
```

### iv) Estimate the 95% CI of the bootstrapped means.
```{r, echo=FALSE}
mean <- mean(bootstrapped_samples)
sd_error <- sd(bootstrapped_samples) / ( length(bootstrapped_samples)^0.5 )
ci95_low <- mean - 1.96 * sd_error
ci95_high <- mean + 1.96 * sd_error
glue("The 95% CI is between {ci95_low} and {ci95_high}")
```

## b) By what time of day, have half the new members of the day already arrived at their restaurant?

### i) Estimate the median of minday
```{r, echo=FALSE}
median(minday)
```

### ii) Visualize the medians of the 2000 bootstrapped samples
```{r, echo=FALSE}
#visualize the bootstrapped samples medians
plot(
  density(minday), 
  col="red", 
  lty = "dashed", 
  main="Medians of the 2000 Bootstrapped Samples"
)

plot_sample_median <- function(sample) {
  abline(
    v=median(sample),
    col="#8cd9db"
  ) 
  
  return(median(sample))
}

sample_medians <- apply(bootstrapped_samples, 2, FUN=plot_sample_median)

abline(
  v=median(minday), 
  col="black"
)

legend(
  "topleft", 
  legend=c("Population", "Population Median", "Bootstrapped Median"), 
  col=c("red", "black", "#8cd9db"), 
  lty = c("dashed", "solid", "solid"), 
  bty = "n", 
  pt.cex = 2, 
  cex = 1.2, 
  text.col = "black", 
  horiz = F 
)
```

```{r, echo=FALSE}
plot(
  density(sample_medians), 
  xlim=c(min(sample_medians)-10, max(sample_medians) + 10),
  main="Bootstrap Medians in Density Plot"
)
```


### iii) Estimate the 95% CI of the bootstrapped medians.
```{r, echo=FALSE}
mean <- mean(sample_medians)
sd_error <- sd(sample_medians) / ( length(sample_medians)^0.5 )
ci95_low <- mean - 1.96 * sd_error
ci95_high <- mean + 1.96 * sd_error
glue("The 95% CI is between {ci95_low} and {ci95_high}")
```