---
title: "BACS HW2"
author: "109062710"
date: "March 17, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
library(ggplot2)
library(glue)
library(gridExtra)
```

# Question 1

Here is the helper functions for Q1
```{r}
density_plot <- function(data, title) {
  ggplot(mapping = aes(data)) +
    geom_density(
      fill="#FC4E07", 
      color="#e9ecef",
    ) +
    ggtitle(title)
}

histogram_plot <- function(data, title) {
  binwidth <- (2 * IQR(data)) / n^(1/3)
  bins <- ceiling(max(data) - min(data)) + binwidth
  
  ggplot(mapping = aes(data)) +
    geom_histogram(
      fill="#FC4E07", 
      color="#e9ecef",
      bins = bins,
      binwidth = binwidth
    ) +
    ggtitle(title)
}
```

## A. create a normal distribution `(mean = 940, sd = 190)` and standardize it
```{r}
n <- 1000
mean <- 940
sd <- 190

rnorm <- rnorm(1000, mean = mean, sd = sd)
rnorm_std <- (rnorm - mean) / sd
```


### i) What should we expect the mean and standard deviation of rnorm_std to be, and why?

```{r}
nonstd_rnorm_mean <- mean(rnorm)
nonstd_rnorm_sd <- sd(rnorm)

std_rnorm_mean <- mean(rnorm_std)
std_rnorm_sd <- sd(rnorm_std)

glue("The mean of non-standardized normal distribution is {nonstd_rnorm_mean}, and its standard deviation is {nonstd_rnorm_sd}.")
glue("The mean of standardized normal distribution is {std_rnorm_mean}, and its standard deviation is {std_rnorm_sd}.")
```

x value is between -3 to 3. each number represent how far (in STD unit) each instance from the mean.

### ii)
```{r}
nonstd_rnorm_hist <- histogram_plot(rnorm, "Non-STD ND Histogram")

nonstd_rnorm_density <- density_plot(rnorm, "Non-STD ND Density")

std_rnorm_hist <- histogram_plot(rnorm_std, "Standardized ND Histogram")

std_rnorm_density <- density_plot(rnorm_std, "Standardized ND Density")

grid.arrange(nonstd_rnorm_hist, nonstd_rnorm_density, std_rnorm_hist, std_rnorm_density, ncol=2, nrow=2)
```

### iii) 
It's called **bell-shaped curved** normal distribution

## B. Create a standardized version of minday from the earlier question (let’s call it minday_std)

# Question 2

# Question 3