---
title: "BACS HW15"
author: '109062710'
date: "6/2/2021"
output: pdf_document
---

```{r, include=FALSE}
library(psych)
```


# Question 1

## a. Show a scree plot of data
```{r}
df <- read.csv("/home/johnbjohn/Documents/git-repos/bacs-hw/hw15/security_questions.csv")
pca <- prcomp(df, scale. = TRUE)
```

Create a noise simulation function
```{r}
noise_simulation <- function(x, y) {
  random_normal_dist <- replicate(y, rnorm(x))
  noise <- data.frame(random_normal_dist)
  eigenvalues <- eigen(cor(noise))$values
  return(eigenvalues)
}
```

```{r}
set.seed(2000)
x <- dim(df)[1]
y <- dim(df)[2]
simulate_noise <- replicate(1, noise_simulation(x, y))
evaluated_mean <- apply(simulate_noise, 1, mean)

screeplot(
  pca, 
  type = "line", 
  col = "black",
  main = "Security Question PCA Scree Plot"
)

lines(evaluated_mean, type = "b", col = "red")

legend(
  6,
  8,
  c("Principal Component Analysis", "Parallel Analysis"),
  lty=c(1,1),
  col = c("black", "red")
)
```

## b. How many dimensions would you retain if we used Parallel Analysis?

I would keep 3 dimensions since the red line intersects the black line at the third column.

# Question 2

```{r}
pca_result <- principal(df, nfactors = 3, rotate = "none", scores = TRUE)
pca_result
```

## a. To which principal components does each question seems to best belong?

\textcolor{red}{Let's set a threshold of 0.7, we then have} `Q1, Q3, Q8, Q9, Q11, Q13, Q14, Q16, Q18` \textcolor{red}{that belong to} `PC1` \textcolor{red}{and the other questions seem to belong to either} `PC2` or `PC3`.

## b. How much variance captured by `PC1`, `PC2`, and `PC3`.

```{r}
summary(pca)$importance[2, c(1:3)]
```

\textcolor{red}{All we need is the first three columns of the second row, which is} `Proprotion of Variance`. 
\textcolor{red}{Thus, the variance explained by the} `PC1` \textcolor{red}{is 51\%,} `PC2` \textcolor{red}{is 8\%, and} `PC3` \textcolor{red}{is 6\%.}
\textcolor{red}{In total,} `PC1`, `PC2`, and `PC3` \textcolor{red}{explain roughly 66\% of total variance.}

## c. Which questions are less than adequately explained by the first 3 principal components?

\textcolor{red}{It's} `Q2` \textcolor{red}{since it has `h2`} \textcolor{red}{of 0.4605433.}

## d. How many measurement items share similar loadings between 2 or more components?

```{r}
evaluate_loadings <- function(df, range) {
  return(
    (
      abs(df[range, 1] - df[range, 2])<0.1 | 
      abs(df[range, 2] - df[range, 3])<0.1 | 
      abs(df[range, 1] - df[range, 3])<0.1
    ) &
    (
      df[range, 1] < 0.7 & 
      df[range, 2] < 0.7 & 
      df[range, 3] < 0.7
    )
  )
}

evaluate_loadings(pca_result$loading, 1:18)
```

\textcolor{red}{Only} `Q4`, `Q12`, and `Q17` \textcolor{red}{share similar loadings between 2 or more components.}

## e. Can you distinguish a ‘meaning’ behind the first principal component from the items that load best upon it? (see the wording of the questions of those items)

\textcolor{red}{The meaning of} `PC1` \textcolor{red}{might not be easy to interpret when we compare it with the wording of the questions.}

# Question 3

## a. Individually, does each `RC` explain the same amount of variance?

```{r}
rc <- principal(df, nfactors = 3, rotate = "varimax", scores = TRUE)$loadings
rc
```

\textcolor{red}{Looking at the proportion variance, we can see} `RC1` \textcolor{red}{is 30\% and} `PC1` \textcolor{red}{is 51\%.}
`RC2` \textcolor{red}{is 19\% and} `PC3` \textcolor{red}{is 8\%. While} `RC3` \textcolor{red}{is 16\% and} `PC3` \textcolor{red}{is 6\%.}
\textcolor{red}{Clearly, they are different.}

## b. Together, do these rotated components explain the same amount of variance like the principal components?

\textcolor{red}{Yes, both the rotated components and the principal components have the same total amount of variances explained.}

## c. do Q4, Q12, and Q17 have more clearly differentiated loadings among rotated components?

```{r}
rc[c(4,12,17), 1:3]
```

\textcolor{red}{Since these rotate components have loading value above 0.7, clearly they are more clearly differentiated.}

## d. Can you interpret the meaning of the three rotated components?

```{r}
rc[rc[, 1] > 0.7, 1]
```

`RC1` \textcolor{red}{means data protection.}

```{r}
rc[rc[, 2] > 0.7, 2]
```

`RC2` \textcolor{red}{means transaction processing.}

```{r}
rc[rc[, 3] > 0.7, 3]
```

`RC3` \textcolor{red}{means providing evidence to protect against its denial.}

## e. If we reduced the number of rotated components, does the meaning of our rotated components change?

```{r}
reduced_rc <- principal(df, nfactors = 2, rotate = "varimax", scores = TRUE)
reduced_rc$loadings[,1][reduced_rc$loadings[,1] > 0.7]
```

\textcolor{red}{Yes. When we decreased} `nfactors` \textcolor{red}{by 1, the number of questions belong to `RC1` would increase. However, the meaning stays the same.}
