---
title: "BACS HW13"
author: "109062710"
date: "5/19/2021"
output: pdf_document
---

```{r, include=FALSE}
library(ISLR)
library(dplyr)
library(ggplot2)
```

Prepare the data set
```{r}
cars_log <- with(Auto, data.frame(log(mpg), log(cylinders), log(displacement),
log(horsepower), log(weight), log(acceleration), year, origin, name))
weight_mean <- mean(cars_log$weight)
names(cars_log) <- names(Auto)
head(cars_log)
```

Convert the numbers in `origin` column into names, namely 1 for USA, 2 for Europe, and 3 for Japan.

```{r}
origins <- c("USA", "Europe", "Japan")
cars_log$origin <- factor(cars_log$origin, labels = origins)
```

# Question 1

## Visualization

### i. Split the data set into lightweight cars and heavyweight cars

A new column will be made called `weight_type` with `1` as a heavy car and `2` as a light car.

```{r}
cars_log <- cars_log %>% mutate(weight_type = ifelse(weight >= mean(weight), 1, 2))
head(cars_log)
```

### ii. Create a scatter plot of mpg vs acceleration

```{r}
ggplot(data = cars_log, aes(x = acceleration, y = mpg, col = factor(weight_type))) +
    geom_point()
```

### iii. Make two seperate regression lines

```{r}
ggplot(data = cars_log, aes(x = acceleration, y = mpg, col = factor(weight_type))) +
    geom_point() +
    geom_smooth(method=lm)
```


## b. Report full summaries of light cars and heavy cars

```{r}
light_cars <- cars_log[cars_log$weight < mean(cars_log$weight), ]
light_cars_lm <- lm(mpg ~ weight + acceleration + year + origin, data = light_cars)
summary(light_cars_lm)
```


```{r}
heavy_cars <- cars_log[cars_log$weight >= mean(cars_log$weight), ]
heavy_cars_lm <- lm(mpg ~ weight + acceleration + year + origin, data = light_cars)
summary(heavy_cars_lm)
```

## c. What do you observe about light vs. heavy cars?

\textcolor{red}{Both light and heavy cars follow the same trend where as the acceleration increases, so as the distance that a car can cover.}

# Question 2

## a. Which is the moderating variable (not graded)?

\textcolor{red}{A moderating variable is a variable that explains the behavior of an independent variable and a dependent variable. In this case, we can see that `weight` affects `acceleration`, and `acceleration` affects `mpg`. Clearly, `acceleration` is the moderating variable.}

## b. Use various regression models

### i. Regression without interaction terms

```{r}
summary(
    lm(
        mpg ~ weight + 
            acceleration +
            year + 
            origin,
        data = cars_log
    )
)
```


### ii. Regression with an interaction between weight and acceleration

```{r}
summary(
    lm(
        mpg ~ 
            weight + 
            acceleration +
            year + 
            origin +
            weight * acceleration,
        data = cars_log
    )
)
```


### iii. Regression with a mean-centered interaction term

```{r}
mean_center <- function(data) {
    return(scale(data, center = TRUE, scale = FALSE))
}

summary(
    lm(
        mean_center(mpg) ~ 
            mean_center(acceleration) +
            mean_center(year)+ 
            mean_center(Auto$origin) + # Auto$origin is in numeric
            mean_center(mpg * acceleration),
        data = cars_log
    )
)
```


### iv. Regression with an orthogonalized interaction term

```{r}
weight_acc_inter_lm <- lm((weight * acceleration) ~ 
                            weight + 
                            acceleration +
                            year + origin, 
                        data = cars_log)
cor(weight_acc_inter_lm$residuals, cars_log$weight)
```


```{r}
cor(weight_acc_inter_lm$residuals, cars_log$acceleration)
```

We can see that both weight and acceleration are orthogonal to each other.

Then we show the linear model summary 
```{r}
summary(
    lm(
        mpg ~ weight + acceleration + year + origin + weight_acc_inter_lm$residual,
        data = cars_log
    )
)
```


## c. What is the correlation between the interaction term and the two variables that are multiplied together?

```{r}
# without interaction
no_interaction_weight <- cor((cars_log$weight * cars_log$acceleration), cars_log$weight)
no_interaction_acceleration = cor((cars_log$weight * cars_log$acceleration), cars_log$acceleration)

# mean-centered weight and acceleration
mean_centered_weight <- cor(mean_center(cars_log$weight) * mean_center(cars_log$acceleration), mean_center(cars_log$weight))
mean_centered_acceleration = cor(mean_center(cars_log$weight) * mean_center(cars_log$acceleration), mean_center(cars_log$acceleration))

# orthogonalized weight and acceleration
orthogonalized_weight <- cor(weight_acc_inter_lm$residuals, cars_log$weight)
orthogonalized_acceleration = cor(weight_acc_inter_lm$residuals, cars_log$acceleration)

correlation_matrix <- matrix(
    c(
        no_interaction_weight,
        no_interaction_acceleration,
        mean_centered_weight,
        mean_centered_acceleration,
        orthogonalized_weight,
        orthogonalized_acceleration
    ),
    ncol = 2, byrow=TRUE
)
```

```{r}
correlation_matrix
```


```{r}
rownames(correlation_matrix) <- c("without interaction", "mean-centered", "orthogonalized")
colnames(correlation_matrix) <- c("weight", "acceleration")
round(correlation_matrix, 5)
```

